Analyzing the impact of social attributes on the success of commit integration

### 2017-02-17 Paper/MSRChallenge2017.tex

This study aims to acknowledge the impact of some of these attributes when it 
comes to the quality of the commits developers write and its success when 
integrating into the project build through Travis CI. The knowledge obtained by 
analyzing how much impact social characteristics have on the success of a commit 
integration will help developers further understand what social attributes are 
better proxies for experience and coding excellence; and it will also help code 
integrators and core team members to know how to prioritize pull requests coming 
from different developers, which of them may have a higher probability of 
integration success based not only on the technical difficulty of the 
integration, but also on social factors that determine the expertise of the 
developer in their integration practices.

@@

Previous studies have identified a relationship between technical and social 
factors and pull request acceptance. In the interest of understanding if these 
relationship will hold with a different success measure such as commit 
integration success, and in order to establish a baseline to compare to, we 
deliver our first research question:
\newline \newline
\textbf{What is the relationship, if any, between technical attributes that 
describe the complexity of a commit (such as files added, tests added, lines of 
code, etc) and the final status of the Travis jobs this commit triggers?}
\newline \newline
Assuming the previous studies hold to this different success measure, and there 
is a relationship between technical attributes and commit integration success, 
we are afterwards interested in knowing if adding social attributes to this 
predictability model will increase the probability of the model asserting 
correctly future instances by knowing not only technical data about the commit 
being pushed but also social attributes of the developer pushing the changes:
\newline \newline
\textbf{Given the dataset described before, are the social attributes gathered 
from the Github profiles of developers who pushed those commits, able to 
increase the predictive power of a model created from the technical dataset?}
\newline \newline
We are also interested in knowing what attributes, either from the technical 
background, the social background, and both combined, are the best proxies for 
knowing what will be the success of the commit integration:
\newline \newline
\textbf{Which attributes (in social data, technical data, and both together) are 
the most decisive in order to know if a commit will be successful or not?}
\newline \newline
Finally, we would like to know if/which social attributes have a significant 
impact in success of commit integration to a project: \todo{I'm not sure what's 
the difference between this RQ and the last one}
\newline \newline
\textbf{Does any of the social attributes have a significant impact in the 
likelihood of commit integration success?}
\newline \newline

>>>>

Similar studies in recent years have analyzed the relationship between social 
and technical factors using different measures of success~\cite{tsay14icse,tsay14fse}. 
This study aims to acknowledge the impact of some of these attributes when it 
comes to the quality of the commits developers write and its success when 
integrating into the project build through Travis CI.

The knowledge obtained by 
analyzing how much impact social characteristics have on the success of a commit 
integration will help developers further understand what social attributes are 
better proxies for experience and coding excellence; and it will also help code 
integrators and core team members to know how to prioritize pull requests coming 
from different developers, which of them may have a higher probability of 
integration success based not only on the technical difficulty of the 
integration, but also on social factors that determine the expertise of the 
developer in their integration practices.

@@

Previous studies have identified a relationship between technical and social 
factors and pull request acceptance. In the interest of understanding if these 
relationship hold with a different success measure such as commit 
integration success, and in order to establish a baseline to compare to, we have created a dataset with technical attributes to be able to analyze the predictiveness of these attributes and its relationship with commit integration success. This way, we are able to create a model

We are afterwards interested in knowing if adding social attributes to this 
predictability model will increase the probability of the model asserting 
correctly future instances by knowing not only technical data about the commit 
being pushed but also social attributes of the developer pushing the changes. Therefore our main research question is presented as follows:
\newline \newline
\textbf{Are the social attributes gathered 
from the Github profiles of developers who push commits, able to 
increase the predictive power of a model created from technical attributes of the pushed commits?}
\newline \newline
Concerning the results of this research question we can also derive parallel important information. For example, we are also interested in knowing what attributes, either from the technical 
background, the social background, and both combined, are the best proxies for 
knowing what will be the success of the commit integration, helping both developers and integrators to find ways to help them check the success likeliness of a commit based on metadata of the commit.
